cvx-flats

### 2020-04-17 neurips-20/cvx-flats.tex
Cleaned up new pass of Thm 1 proof

\begin{theorem}\label{thm:cvx-flats}
	Suppose we are given a property $\gamma$.
	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
\end{theorem}
\begin{proof}[Proof intuition]
	\jessie{BTW: $n$, or $\|p\|_0$?}
	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.

	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e. $L$ indirectly elicits $\gamma$.
	Fix any $p \in \simplex$, and take any $r \in \gamma(p)$.
	We argue that there must be some $u \in \Gamma(p) \subset \reals^d$ such that $r = \psi(u)$.
	We know that $r \in \gamma(p) \iff u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.

@@

	\jessiet{This next paragraph is mostly me spelling it out for myself}
	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
	Moreover, we must have $F \cap \simplex \subseteq \gamma_r$.
	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, so $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.

>>>>

\begin{theorem}\label{thm:cvx-flats}
	Suppose we are given a property $\gamma$.
	Fix $p \in \simplex$, and let $r$ be a report such that $p \in \gamma_r$.  
	If there is no $(n - d - 1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$, then there is no convex surrogate loss $L : \reals^d \times \Y \to \reals$ that indirectly elicits $\gamma$.
	Moreover, this must hold for all $p \in \simplex$ and $r \in \gamma(p)$.
\end{theorem}
\begin{proof}[Proof intuition]
	We prove the contrapositive; if there is a surrogate loss $L$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is an $(n-d-1)$-dimensional flat $F$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.

	Suppose we have $L:\reals^d \times \Y \to \reals$ eliciting $\Gamma$ and link $\psi : \reals^d \to \R$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, i.e. $L$ also indirectly elicits $\gamma$.
	Fix $p \in \simplex$, and take any $u \in \Gamma(p)$ such that $\psi(u) = r \in \gamma(p)$.
	We know that $u \in \Gamma(p) \iff \vec 0 \in \partial L(u; p) \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the nonnegative weighted Minkowski sum by convex analysis results \jessie{And mild assumptions on the loss?}.

@@

	\jessiet{This next paragraph is mostly me spelling it out for myself}
	Observe that $F := \ker(W)$ is at most $(n-d-1)$ dimensions in probability space and contains $p$ by construction.
	We also claim that $F \cap \simplex \subseteq \gamma_r$.
	To see this, consider $q \in F \cap \simplex$, but $q \not \in \gamma_r$.
	That would mean that $Wq = \vec 0$, which implies $\vec 0 \in \partial L(u;q)$, implying $q \in \Gamma_u$.
	Therefore, $q \not \in \gamma_r$ would contradict $L$ indirectly eliciting $\gamma$.
